A multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-05-22 manuscript/manuscript.tex
glossary

%  ALWAYS USE THE referee OPTION WITH PAPERS SUBMITTED TO BIOMETRICS!!!
%  You can see what your paper would look like typeset by removing
%  the referee option.  Because the typeset version will be in two
%  columns, however, some of your equations may be too long. DO NOT
%  use the \longequation option discussed in the user guide!!!  This option
%  is reserved ONLY for equations that are impossible to split across 
%  multiple lines; e.g., a very wide matrix.  Instead, type your equations 
%  so that they stay in one column and are split across several lines, 
%  as are almost all equations in the journal.  Use a recent version of the
%  journal as a guide. 
%  
\documentclass[useAMS,referee]{biom}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{blindtext}

@@

>>>>

%  ALWAYS USE THE referee OPTION WITH PAPERS SUBMITTED TO BIOMETRICS!!!
%  You can see what your paper would look like typeset by removing
%  the referee option.  Because the typeset version will be in two
%  columns, however, some of your equations may be too long. DO NOT
%  use the \longequation option discussed in the user guide!!!  This option
%  is reserved ONLY for equations that are impossible to split across 
%  multiple lines; e.g., a very wide matrix.  Instead, type your equations 
%  so that they stay in one column and are split across several lines, 
%  as are almost all equations in the journal.  Use a recent version of the
%  journal as a guide. 
%  
\documentclass[useAMS,referee]{biom}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{booktabs}

@@

\begin{itemize}

    \item $\mathbf{Y}$: A $n \times p$ matrix containing all multivariate skew-normal regression outcomes such that $y_{ij}$ is the $j^{th}$ outcome observed for subject $i$, where $i = 1,...,n$ and $j = 1,...p$.

    \item $\mathbf{X}$: A $n \times m$ matrix containing all multivariate skew-normal regression covariates such that $x_{ij}$ is the $j^{th}$ covariate value for subject $i$.

    \item $\mathbf{B}$: A $m \times p$ matrix containing all multivariate skew-normal regression coefficients such that $\mathbf{B} = \left [ \boldsymbol\beta_1,...,\boldsymbol\beta_p \right ]$, where $\beta_{ij}$ is interpreted as the effect of covariate $i$ on outcome $j$ for $i = 1,...,m$ and $j = 1,...,p$.

    \item $\mathbf{E}$: A $n \times p$ matrix of error terms in the multivariate skew-normal regression model component. $\mathbf{E}$ is made up of row vectors $\boldsymbol\epsilon_i = (\epsilon_{i1},...,\epsilon_{ip})$, where $ \boldsymbol\epsilon_i \stackrel{iid}{\sim} N_p(0, \boldsymbol\Sigma)$ for $i = 1,...,n$.

    \item $\boldsymbol\Sigma$: A $p \times p$ covariance matrix that defines the correlation between the $p$ multivariate normal outcomes.

    \item $\boldsymbol\Omega$: A $p \times p$ covariance scale matrix that defines the correlation between the $p$ multivariate skew-normal outcomes.

    \item $\boldsymbol\psi$: A $p \times 1$ vector containing the skewness parameter for each outcome.

    \item $\boldsymbol\alpha$: A $p \times 1$ vector containing the skewness parameter for each outcome.

    \item $\mathbf{t}$: A $n \times 1$ vector of truncated normal random effects used in the stochastic representation of the multivariate skew-normal distribution. For $i = 1,...,n$, $t_i \stackrel{iid}{\sim}T_[0,\infty)(0,1)$

    \item $\mathbf{X}^*$: A $n \times (m + 1)$ matrix constructed by column binding $\mathbf{t}$ to $\mathbf{X}$

    \item $\mathbf{B}^*$: A $(m+1) \times p$ matrix constructed by row binding $\boldsymbol\psi^T$. to $\mathbf{B}$.

\end{itemize}
